Neural Connectome of the Ctenophore Statocyst

### 2025-06-23 manuscript/Manuscript.qmd
MS: edit
Fig 1: fix n cells, ms edit

---
title: "Neural Connectome of the Ctenophore Statocyst"
subtitle: |
  **Kei Jokura**$^{1,2,3,4,5*}$, **Sanja Jasek**$^{1,2,6}$, **Lara Niederhuas**$^{6}$, **Pawel Burkhardt**$^{7}$, **Gáspár Jékely**$^{1,2,6,*}$  
  <br><br>  
  $^{1}$ Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom  
  <br>
  $^{2}$ Biosciences, Faculty of Health and Life Sciences, University of Exeter, Exeter EX4 4QD, UK
  <br>  
  $^{3}$ Grass Laboratory, Marine Biological Laboratory, Woods Hole, MA 02543, USA  
  <br> 
  $^{4}$ Exploratory Research Center on Life and Living Systems (ExCELLS), Okazaki, 444-8787, Japan  
  <br>  
  $^{5}$ National Institute for Basic Biology (NIBB), Okazaki, 444-8585, Japan  
  <br> 
  $^{6}$ Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany  
  <br>
  $^{7}$ Michael Sars Centre, University of Bergen, Norway
  <br><br>  
    **$^{*}$ Correspondence:**  ![](pictures/emails.png){width=30em}
mainfont: Luciola-Math
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true
    css: style.css 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

>>>>

---
title: "Neural Connectome of the Ctenophore Statocyst"
subtitle: |
  **Kei Jokura**$^{1,2,3,4,5*}$, **Sanja Jasek**$^{1,2,6}$, **Lara Niederhaus**$^{6}$, **Pawel Burkhardt**$^{7}$, **Gáspár Jékely**$^{1,2,6,*}$  
  <br><br>  
  $^{1}$ Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom  
  <br>
  $^{2}$ Biosciences, Faculty of Health and Life Sciences, University of Exeter, Exeter EX4 4QD, UK
  <br>  
  $^{3}$ Grass Laboratory, Marine Biological Laboratory, Woods Hole, MA 02543, USA  
  <br> 
  $^{4}$ Exploratory Research Center on Life and Living Systems (ExCELLS), Okazaki, 444-8787, Japan  
  <br>  
  $^{5}$ National Institute for Basic Biology (NIBB), Okazaki, 444-8585, Japan  
  <br> 
  $^{6}$ Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany  
  <br>
  $^{7}$ Michael Sars Centre, University of Bergen, Norway
  <br><br>  
    **$^{*}$ Correspondence:**  ![](pictures/emails.png){width=30em}
mainfont: Luciola-Math
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true
    css: style.css 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---
